OSF management

### 2022-04-15 osf/manage-osf.Rmd
✨ - fix up code for downloading teams components

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
knitr::opts_knit$set(root.dir = here::here())
library(here)
library(tidyverse)
library(osfr)
library(speakr)
```

@@

```{r teams-download, eval=FALSE}
osf_teams <- osf_retrieve_node("n3fyd")
teams_comps <- osf_ls_nodes(osf_teams, n_max = Inf)
```

>>>>

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, eval = FALSE)
knitr::opts_knit$set(root.dir = here::here())
library(here)
library(tidyverse)
library(osfr)
library(speakr)
library(glue)
library(googlesheets4)
```

@@

```{r teams-comps, eval=FALSE}
osf_teams <- osf_retrieve_node("n3fyd")
# Warning, takes a minute
teams_comps <- osf_ls_nodes(osf_teams, n_max = Inf)
assigned <- read_sheet("https://docs.google.com/spreadsheets/d/1OOXB-8Uk-fh_urw0Lm4DC0jBueXLIb4Bm-a9--UVXOw/edit?usp=sharing")
```

```{r teams-download, eval=FALSE}
my_assignment <- assigned %>%
  # ste, joseph, or timo
  filter(assigned_to == "ste") %>%
  pull(animal)

for (team in 1:length(my_assignment)) {
  skip_to_next <- FALSE

  name <- my_assignment[team]
  dir.create(glue("./data/teams_analyses/{name}"), recursive = TRUE, showWarnings = FALSE)

  tryCatch(
    osf_ls_files(teams_comps[team,], type = "folder") %>%
      osf_download(
        path = glue("./data/teams_analyses/{name}"),
        recurse = TRUE, verbose = TRUE, progress = TRUE, conflicts = "skip"
      ),
    error = function(e) { skip_to_next <<- TRUE}
  )

  if(skip_to_next) { next }
}
```
